IRS-Aided SWIPT: Joint Waveform, Active and Passive Beamforming Design

### 2020-10-28 main.tex
:construction: Update parameters

	\begin{section}{Performance Evaluations}\label{se:performance_evaluation}
		\begin{figure}[!t]
			\centering
			\def\svgwidth{\columnwidth}
			\import{assets/}{layout.pdf_tex}
			\caption{System layout in the simulation.}
			\label{fi:layout}
		\end{figure}
		To evaluate the performance of the proposed IRS-aided SWIPT system, we characterize the average R-E regions under typical setups. Consider a large open space WiFi-like environment at a center frequency of \SI{5.18}{\GHz} with reference bandwidth $B=1\,\si{\MHz}$. As shown in Fig.~\ref{fi:layout}, we assume the IRS moves along a horizontal line parallel to the AP-user path and let $d_H$, $d_V$ be the horizontal and vertical distances from the AP to the IRS, respectively. We also denote $d_D$, $d_I$, $d_R$ as the length of direct, incident, reflective paths such that $d_I=\sqrt{d_H^2+d_V^2}$, $d_R=\sqrt{(d_D-d_H)^2+d_V^2}$. Choose $d_D=15\,\si{\meter}$, $d_V=2\,\si{\meter}$ and reference $d_H=2\,\si{\meter}$. The path loss and fading parameters are obtained from IEEE TGn channel model D \cite{Erceg2004}, and reference path loss is set to $L_0=-35\,\si{\dB}$ at $d_0=1\,\si{\meter}$. We assume all channels are NLoS with taps modelled as i.i.d. CSCG random variables of unit average sum-power to create a normalized multipath response. The reference numbers of transmit antennas, IRS reflectors and subbands are $M=1$, $L=20$, $N=16$, respectively. No spatial correlation is considered across transmit antennas and IRS arrays. Rectenna parameters are taken as $k_2=0.0034$, $k_4=0.3829$, $R_{\text{ant}}=50\,\si{\ohm}$. With \SI{0}{\dBi} transmit antenna gain, the average Effective Isotropic Radiated Power (EIRP) is fixed to $P=-36\,\si{\dBm}$ while the reference average noise power is $\sigma_n=-40\,\si{\dBm}$ at all subbands. We also assume \SI{0}{\dBi} IRS element gain and \SI{2}{\dBi} receive antenna gain. For the algorithm, the tolerance is $\epsilon=10^{-8}$, the number of candidates in the Gaussian randomization method is $Q=10^{3}$, and the R-E region is averaged over \num{200} channel realizations. In the R-E boundary, the leftmost point corresponds to WPT ($\rho=1$) where power can be allocated simultaneously to modulated and unmodulated waveform to maximize the average output DC current. On the other hand, the rightmost point corresponds to WIT ($\rho=0$) where the solution coincides with the Water-Filling (WF) algorithm that allocates all power to modulated waveform only. For a fair comparison, the $x$-axis of the plots has been normalized to per-subband rate.

@@

		\begin{figure}[!t]
			\centering
			\begin{adjustbox}{width=\linewidth}
				\input{assets/re_subband.tex}
			\end{adjustbox}
			\caption{Average R-E region versus $N$ for $M=1$, $L=20$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_H=2\,\si{\meter}$.}
			\label{fi:re_subband}
		\end{figure}

		\begin{figure}[!t]
			\centering
			\begin{adjustbox}{width=\linewidth}
				\input{assets/waveform_subband.tex}
			\end{adjustbox}
			\caption{WPT-optimized waveform amplitudes versus $N$ for $M=1$, $L=20$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_H=2\,\si{\meter}$.}
			\label{fi:waveform_subband}
		\end{figure}

@@

		\begin{figure}[!t]
			\centering
			\begin{adjustbox}{width=\linewidth}
				\input{assets/re_noise.tex}
			\end{adjustbox}
			\caption{Average R-E region and splitting ratio versus $\sigma_n$ for $M=1$, $N=16$, $L=20$, $B=1\,\si{\MHz}$ and $d_H=2\,\si{\meter}$.}
			\label{fi:re_noise}
		\end{figure}

@@

		\begin{figure}[!t]
			\centering
			\begin{adjustbox}{width=\linewidth}
				\input{assets/re_distance.tex}
			\end{adjustbox}
			\caption{Average R-E region versus $d_H$ for $M=1$, $N=16$, $L=20$, $\sigma_n=-40\,\si{\dBm}$ and $B=1\,\si{\MHz}$.}
			\label{fi:re_distance}
		\end{figure}

@@

		\begin{figure}[!t]
			\centering
			\begin{adjustbox}{width=\linewidth}
				\input{assets/re_tx.tex}
			\end{adjustbox}
			\caption{Average R-E region versus $M$ for $N=16$, $L=20$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_H=2\,\si{\meter}$.}
			\label{fi:re_tx}
		\end{figure}

		\begin{figure}[!t]
			\centering
			\begin{adjustbox}{width=\linewidth}
				\input{assets/re_reflector.tex}
			\end{adjustbox}
			\caption{Average R-E region versus $L$ for $M=1$, $N=16$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_H=2\,\si{\meter}$.}
			\label{fi:re_reflector}
		\end{figure}

		\begin{figure}[!t]
			\centering
			\begin{adjustbox}{width=\linewidth}
				\input{assets/scaling_tx.tex}
			\end{adjustbox}
			\caption{Average WIT SNR and WPT DC current versus $M$ for $N=16$, $L=20$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_H=\text{[TODO]}\,\si{\meter}$.}
			\label{fi:scaling_tx}
		\end{figure}

		\begin{figure}[!t]
			\centering
			\begin{adjustbox}{width=\linewidth}
				\input{assets/scaling_reflector.tex}
			\end{adjustbox}
			\caption{Average WIT SNR and WPT DC current versus $L$ for $M=1$, $N=16$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_H=\text{[TODO]}\,\si{\meter}$.}
			\label{fi:scaling_reflector}
		\end{figure}

@@

		\begin{figure}[!t]
			\centering
			\begin{adjustbox}{width=\linewidth}
				\input{assets/re_irs_1mhz.tex}
			\end{adjustbox}
			\caption{Average R-E region for adaptive, ideal, fixed and no IRS over $B=1\,\si{\MHz}$ for $M=1$, $N=16$, $L=20$, $\sigma_n=-40\,\si{\dBm}$ and $d_H=2\,\si{\meter}$.}
			\label{fi:re_irs_1mhz}
		\end{figure}

		\begin{figure}[!t]
			\centering
			\begin{adjustbox}{width=\linewidth}
				\input{assets/re_irs_10mhz.tex}
			\end{adjustbox}
			\caption{Average R-E region for adaptive, ideal, fixed and no IRS over $B=10\,\si{\MHz}$ for $M=1$, $N=16$, $L=20$, $\sigma_n=-40\,\si{\dBm}$ and $d_H=2\,\si{\meter}$.}
			\label{fi:re_irs_10mhz}
		\end{figure}

>>>>

	\begin{section}{Performance Evaluations}\label{se:performance_evaluation}
		\begin{figure}[!t]
			\centering
			\def\svgwidth{\columnwidth}
			\import{assets/}{layout.pdf_tex}
			\caption{System layout in the simulation.}
			\label{fi:layout}
		\end{figure}
		To evaluate the performance of the proposed IRS-aided SWIPT system, we characterize the average R-E regions under typical setups. Consider a large open space WiFi-like environment at a center frequency of \SI{5.18}{\GHz} with reference bandwidth $B=1\,\si{\MHz}$. As shown in Fig.~\ref{fi:layout}, we assume the IRS moves along a horizontal line parallel to the AP-user path and let $d_H$, $d_V$ be the horizontal and vertical distances from the AP to the IRS, respectively. We also denote $d_D$, $d_I$, $d_R$ as the length of direct, incident, reflective paths such that $d_I=\sqrt{d_H^2+d_V^2}$, $d_R=\sqrt{(d_D-d_H)^2+d_V^2}$. Choose as reference $d_D=15\,\si{\meter}$, $d_V=2\,\si{\meter}$ and $d_H=2\,\si{\meter}$. The path loss and fading parameters are obtained from IEEE TGn channel model D \cite{Erceg2004}, and reference path loss is set to $L_0=-35\,\si{\dB}$ at $d_0=1\,\si{\meter}$. We assume all channels are NLoS with taps modelled as i.i.d. CSCG random variables of unit average sum-power to create a normalized multipath response. The reference numbers of transmit antennas, IRS reflectors and subbands are $M=1$, $L=20$, $N=16$, respectively. No spatial correlation is considered across transmit antennas and IRS arrays. Rectenna parameters are taken as $k_2=0.0034$, $k_4=0.3829$, $R_{\text{ant}}=50\,\si{\ohm}$. With \SI{0}{\dBi} transmit antenna gain, the average Effective Isotropic Radiated Power (EIRP) is fixed to $P=-36\,\si{\dBm}$ while the reference average noise power is $\sigma_n=-40\,\si{\dBm}$ at all subbands. We also assume \SI{0}{\dBi} IRS element gain and \SI{2}{\dBi} receive antenna gain. For the algorithm, the tolerance is $\epsilon=10^{-8}$, the number of candidates in the Gaussian randomization method is $Q=10^{3}$, and the R-E region is averaged over \num{200} channel realizations. In the R-E boundary, the leftmost point corresponds to WPT ($\rho=1$) where power can be allocated simultaneously to modulated and unmodulated waveform to maximize the average output DC current. On the other hand, the rightmost point corresponds to WIT ($\rho=0$) where the solution coincides with the Water-Filling (WF) algorithm that allocates all power to modulated waveform only. For a fair comparison, the $x$-axis of the plots has been normalized to per-subband rate.

@@

		\begin{figure}[!t]
			\centering
			\begin{adjustbox}{width=\linewidth}
				\input{assets/re_subband.tex}
			\end{adjustbox}
			\caption{Average R-E region versus $N$ for $M=1$, $L=20$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_H=d_V=2\,\si{\meter}$.}
			\label{fi:re_subband}
		\end{figure}

		\begin{figure}[!t]
			\centering
			\begin{adjustbox}{width=\linewidth}
				\input{assets/waveform_subband.tex}
			\end{adjustbox}
			\caption{WPT-optimized waveform amplitudes versus $N$ for $M=1$, $L=20$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_H=d_V=2\,\si{\meter}$.}
			\label{fi:waveform_subband}
		\end{figure}

@@

		\begin{figure}[!t]
			\centering
			\begin{adjustbox}{width=\linewidth}
				\input{assets/re_noise.tex}
			\end{adjustbox}
			\caption{Average R-E region and splitting ratio versus $\sigma_n$ for $M=1$, $N=16$, $L=20$, $B=1\,\si{\MHz}$ and $d_H=d_V=2\,\si{\meter}$.}
			\label{fi:re_noise}
		\end{figure}

@@

		\begin{figure}[!t]
			\centering
			\begin{adjustbox}{width=\linewidth}
				\input{assets/re_distance.tex}
			\end{adjustbox}
			\caption{Average R-E region versus $d_H$ for $M=1$, $N=16$, $L=20$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_V=2\,\si{\meter}$.}
			\label{fi:re_distance}
		\end{figure}

@@

		\begin{figure}[!t]
			\centering
			\begin{adjustbox}{width=\linewidth}
				\input{assets/re_tx.tex}
			\end{adjustbox}
			\caption{Average R-E region versus $M$ for $N=16$, $L=20$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_H=d_V=2\,\si{\meter}$.}
			\label{fi:re_tx}
		\end{figure}

		\begin{figure}[!t]
			\centering
			\begin{adjustbox}{width=\linewidth}
				\input{assets/re_reflector.tex}
			\end{adjustbox}
			\caption{Average R-E region versus $L$ for $M=1$, $N=16$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_H=d_V=2\,\si{\meter}$.}
			\label{fi:re_reflector}
		\end{figure}

		\begin{figure}[!t]
			\centering
			\begin{adjustbox}{width=\linewidth}
				\input{assets/scaling_tx.tex}
			\end{adjustbox}
			\caption{Average WIT SNR and WPT DC current versus $M$ for $N=16$, $L=20$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$, $d_H=0$ and $d_V=0.5\,\si{\meter}$.}
			\label{fi:scaling_tx}
		\end{figure}

		\begin{figure}[!t]
			\centering
			\begin{adjustbox}{width=\linewidth}
				\input{assets/scaling_reflector.tex}
			\end{adjustbox}
			\caption{Average WIT SNR and WPT DC current versus $L$ for $M=1$, $N=16$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$, $d_H=0$ and $d_V=0.5\,\si{\meter}$.}
			\label{fi:scaling_reflector}
		\end{figure}

@@

		\begin{figure}[!t]
			\centering
			\begin{adjustbox}{width=\linewidth}
				\input{assets/re_irs_1mhz.tex}
			\end{adjustbox}
			\caption{Average R-E region for adaptive, ideal, fixed and no IRS over $B=1\,\si{\MHz}$ for $M=1$, $N=16$, $L=20$, $\sigma_n=-40\,\si{\dBm}$ and $d_H=d_V=2\,\si{\meter}$.}
			\label{fi:re_irs_1mhz}
		\end{figure}

		\begin{figure}[!t]
			\centering
			\begin{adjustbox}{width=\linewidth}
				\input{assets/re_irs_10mhz.tex}
			\end{adjustbox}
			\caption{Average R-E region for adaptive, ideal, fixed and no IRS over $B=10\,\si{\MHz}$ for $M=1$, $N=16$, $L=20$, $\sigma_n=-40\,\si{\dBm}$ and $d_H=d_V=2\,\si{\meter}$.}
			\label{fi:re_irs_10mhz}
		\end{figure}
